\systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2019-04-10 archive.tex
regex text from Max

>>>>

For this task, we used the dataset from [cite Luke], consisting of a
large corpus of string concepts. Each string concept has 5 ``train"
strings and 5 ``test" strings.

We trained \system using 128 string concepts, randomly sampled from
the corpus, and tested on another 128 randomly sampled string
concepts.

Our initial DSL consisted of all printable characters, four special
character classes (lowercase letters $\\l$, uppercase letters $\\u$,
digits $\\d$, and '.', which represents all possible characters), and
3 functions: \textbf{Kleene Star}, \textbf{Maybe}, \textbf{Or}. We
also included a task-dependent 'constant' token, which prints the
largest constant string shared across the 5 training tasks.
Concatenation was done via continuation-style, as above in the logo
domain ... [idk how you wanted this to be mentioned?]

Because this domain has a relatively large number of parameters, we
used a modified version of the recognition model, where only unigram
parameters were inferred. We found that this recognition model trained
quicker and more had more stable convergence.

Probabilistic regexes have no ground truth notion of ``solved," so we
evaluate differently from other domains. Our main evaluation metric is
to report a lower bound on the posterior predictive of each task given
the learned grammar:

\begin{align} 
\Probablility[x_{test}|x_{train}, \mathcal D , \theta ] &= \integral
dp \Probability[x_{test}| p] \Probablility[p| x_{train}, \mathcal D ,
\theta]\\
&= \integral dp \Probability[x_{test}| p] \Probablility[x_{train}|p]
\Probablility[p|\mathcal D , \theta]\\
\geq& \sum_{p\in F} \Probability[x_{test}| p] \Probablility[x_
{train}|p] \Probablility[p|\mathcal D , \theta]
\end{align}

%\begin{align} 
%\Probablility[x|\mathcal D , \theta ] &= \integral dp \Probablility
[x|p] \Probablility[p|\mathcal D , \theta]\\
%\geq& \sum_{p\in F} \Probablility[x|p] \Probablility[p|\mathcal D ,
\theta]
%\end{align}

where $x_{train}$ are the training strings for task $x$, and $x_
{test}$ are the held-out test strings, not seen during search.

For this domain we use an additional post-processing step, in order to
generate realistic samples from the probabilistic programs. For each
task and each found probabilistic regex, we separately optimize the
continuous regex production parameters in order to maximize the
likelihood on the training strings for that task. We apply additive
smoothing to ensure optimization does not over-fit to the training
tasks.
